---
title: "Statistics 133 Final Project"
author: "Christian Alarcio, Ellen Chan, Anais Sidhu, Ruomeng (Michelle) Yang"
date: "December 7, 2015"
output: pdf_document
---

#Introduction

Our findings and analysis from this project were led by our hypothesis:

\em{Technology industries show higher growth and higher beta, and therefore lower P/E ratios.}

We answered the following questions:

- What is the relationship between beta and the payout percentage?
- What is the relationship between beta and expected growth rate?

Before we introduce our dataset and preprocessing steps, here is an explanation of some of the financial terminology.

<insert terminology>

#Dataset & Preprocessing

To begin the project, two datasets were downloaded as CSV files from the NYU Stern Business School's data archives. There was an online link that automatically downloaded the data we needed, so no there was no R needed. We start by setting the working directory, then reading the two CSV files. The files were then merged and assigned to the data frame "raw_data".

```{r, eval=TRUE, tidy=TRUE}
# Set working directory
setwd("~/Documents/UC\ Berkeley\ 2015-2016/Statistics\ 133/projects/final/")

# Extract raw data
beta <- read.csv("raw_data/total_beta.csv", header = TRUE,  stringsAsFactors = FALSE)
pe <- read.csv("raw_data/pe_data.csv", header = TRUE, stringsAsFactors = FALSE)

# Combine data from the two files
raw_data <- merge(beta, pe, by = intersect(names(beta), names(pe)))
```

We then inspected the contents of the data frame.

```{r, tidy=TRUE}
# Inspect merged data
head(raw_data)
summary(raw_data)
names(raw_data)
str(raw_data)

# Inspect individual elements of the merged data
print("Summary of elements in raw_data")
for (i in 1:length(raw_data)) {
    print(paste0("Summary of ", names(raw_data)[i], ":"))
    print(summary(raw_data[, i]))
}
```

Further inspection revealed that column "X" is a column full of NA values We start to clean data by removing this column through subsetting and reassigning this subset as the dataframe "clean_data".

```{r, eval=TRUE, tidy=TRUE}
# Remove blank columns
clean_data <- subset(raw_data, select = -X)
```

We also find that some columns have unideal names, which we rename.

```{r, eval=TRUE, tidy=TRUE}
# Rename column titled Aggregate.Mkt.Cap..Net.Income
clean_data$Aggregate.Mkt.Cap.Net.Income <- clean_data$Aggregate.Mkt.Cap..Net.Income
clean_data$Aggregate.Mkt.Cap..Net.Income <- NULL

# Rename column titled clean_data$Aggregate.Mkt.Cap..Trailing.Net.Income
clean_data$Aggregate.Mkt.Cap.Trailing.Net.Income <- clean_data$Aggregate.Mkt.Cap..Trailing.Net.Income
clean_data$Aggregate.Mkt.Cap..Trailing.Net.Income <- NULL

# Rename column titled Number.of.firms
clean_data$Number.of.Firms <- clean_data$Number.of.firms
clean_data$Number.of.firms <- NULL
```

We then turn the two character columns, Average Correlation and Expected Growth in Next 5 Years, into numeric vectors for more accurate analysis of numbers.

```{r, eval=TRUE, tidy=TRUE}
# Rename column titled Average.correlation and turn it into a numeric column vector
clean_data$Average.Correlation <- as.numeric(gsub("%", "", clean_data$Average.correlation))
clean_data$Average.correlation <- NULL
head(clean_data$Average.Correlation)

# Rename column titled Expected.growth...next.5.years and turn it into a numeric column vector
clean_data$Expected.Growth.Next.5.Years <- as.numeric(gsub("%", "", clean_data$Expected.growth...next.5.years))
clean_data$Expected.growth...next.5.years <- NULL
head(clean_data$Expected.Growth.Next.5.Years)
```

Then, we proceed to removing rows that contain data that cannot be evaluated or will not aid in our analysis. We found that the row "Unclassified" would fit that description. We also considered removing "Total Market", since that did not pertain to the entire industry but is simply an aggregate of all other industries.

```{r, eval=TRUE, tidy=TRUE}
# Make copy of clean_data without the row "Unclassified"
clean_data <- clean_data[-which(clean_data$Industry == "Unclassified"),]

# Make copy of clean_data without the row "Unclassified" or "Total Market"
industries_only <- clean_data[-which(clean_data$Industry == "Unclassified" | clean_data$Industry == "Total Market"),]
```

We then inspect elements of our cleaned datasets.

```{r, eval=TRUE, tidy=TRUE}
# Inspect elements of the final clean_data and industries_only
print("Summary of elements in clean_data")
for (i in 1:length(clean_data)) {
    print(paste0("Summary of ", names(clean_data)[i], ":"))
    print(summary(clean_data[, i]))
}

print("Summary of elements in industries_only")
for (i in 1:length(industries_only)) {
    print(paste0("Summary of ", names(industries_only)[i], ":"))
    print(summary(industries_only[, i]))
}

# Basic plots of variables
plot(clean_data$Average.Unlevered.Beta)
plot(clean_data$Average.Levered.Beta)
plot(clean_data$Current.PE)
plot(clean_data$Forward.PE)
plot(clean_data$PEG.Ratio)
plot(clean_data$Average.Correlation)
plot(clean_data$Expected.Growth.Next.5.Years)

# Exploration of industries that have certain maximum and minimum values
clean_data[which.max(clean_data$Average.Unlevered.Beta), "Industry"]
clean_data[which.min(clean_data$Average.Unlevered.Beta), "Industry"]
clean_data[which.max(clean_data$Average.Levered.Beta), "Industry"]
clean_data[which.min(clean_data$Average.Levered.Beta), "Industry"]
clean_data[which.max(clean_data$Current.PE), "Industry"]
clean_data[which.min(clean_data$Current.PE), "Industry"]
clean_data[which.max(clean_data$PEG.Ratio), "Industry"]
clean_data[which.min(clean_data$PEG.Ratio), "Industry"]
clean_data[which.max(clean_data$Expected.Growth.Next.5.Years), "Industry"]
clean_data[which.min(clean_data$Expected.Growth.Next.5.Years), "Industry"]

# Histograms of select variables
hist(clean_data$Average.Unlevered.Beta,
     main = "Histogram of Average Unlevered Beta",
     xlab = "Average Unlevered Beta")
hist(clean_data$Average.Levered.Beta,
     main = "Histogram of Average Levered Beta",
     xlab = "Average Levered Beta")
hist(clean_data$PEG.Ratio,
     main = "Histogram of PEG Ratio",
     xlab = "PEG Ratio")
hist(clean_data$Expected.Growth.Next.5.Years,
     main = "Histogram of Expected Growth in the Next 5 Years",
     xlab = "Expected Growth in the Next 5 Years")
```

Finally, we create CSV files for our cleaned data and placed it into the clean_data directory.

```{r, eval=FALSE}
# Create CSV files for clean data
file.create("clean_data/clean_data.csv")
write.csv(clean_data, file = "clean_data/clean_data.csv")
file.create("clean_data/industries_only.csv")
write.csv(industries_only, file = "clean_data/industries_only.csv")
```

#Methods & Analysis

Before we can analyze our data, we will first need to set up the packages and dependencies we will be using. We will also need to retrieve and read our clean dataset.

```{r, eval=TRUE, tidy=TRUE}
# Set working directory back for knitting
setwd("/Users/Michelle/Documents/UC Berkeley 2015-2016/Statistics 133/projects/final/report")

# Set up ggplot2
library(ggplot2)
dev.off()

# Set up readr
library(readr)

# Set up scatterplot3d
library(scatterplot3d)

# Set up stringr
library(stringr)

# Set correct working directory again
setwd("~/Documents/UC\ Berkeley\ 2015-2016/Statistics\ 133/projects/final/")

# Read data files
clean_data <- read.csv("clean_data/clean_data.csv", header = TRUE, stringsAsFactors = FALSE)
industries_only <- read.csv("clean_data/industries_only.csv", header = TRUE, stringsAsFactors = FALSE)
```


------ ELLEN ------------
```{r, eval=TRUE, tidy=TRUE}
# Scatter plot of Current PE to Forward PE
ggplot(clean_data, aes(x = Current.PE, y = Forward.PE)) +
    geom_point(color = rgb(100, 200, 200, 100, maxColorValue = 255)) + 
    ggtitle("Current PE Ratio vs. Forward PE Ratio") + xlab("Current PE Ratio") +
    ylab("Foward PE Ratio") + theme_classic()

# Bar plot of Current PE, Forward PE, Total Levered Beta, and Expected
# Growth in the Next 5 Years
barplot(clean_data$Current.PE, border = NA, xlab = "Current PE", ylab = "Frequency",
        col = rgb(200, 100, 100, 100, maxColorValue = 255),
        main = "Bar Plot of Current PE Ratio")
barplot(clean_data$Forward.PE, border = NA, xlab = "Foward PE", ylab = "Frequency",
        col = rgb(200, 100, 200, 100, maxColorValue = 255),
        main = "Bar Plot of Forward PE Ratio")
barplot(clean_data$Total.Levered.Beta, border = NA, xlab = "Total levered beta",
        ylab = "Frequency", col = rgb(0, 150, 150, 100, maxColorValue = 255),
        main = "Bar Plot of Total Levered Beta")
barplot(clean_data$Expected.Growth.Next.5.Years, border = NA,
        xlab = "Expected growth rate (next 5 years)", ylab = "Frequency",
        col = rgb(150, 150, 250, 100, maxColorValue = 255),
        main = "Bar Plot of Forward PE Ratio")

# Analyze which industries are in the highest and lowest beta interval
beta_intervals <- seq(from = 0, to = 1.5, by = 0.3)
interval_fun <- function(beta) {
    for (i in 1:5) {
        if (beta_intervals[i] < beta & beta < beta_intervals[i + 1]) {
            return (i)
        }
    }
}
beta_interval <- unlist(lapply(clean_data$Average.Unlevered.Beta,
                               FUN = interval_fun))
as.vector(clean_data$Industry[unlist(beta_interval) == 5])
as.vector(clean_data$Industry[unlist(beta_interval) == 1])
```

We find that we have 8 industries in the highest beta interval, which are companies in growing markets such as online retail, real estate, etc. Companies with lowest beta are stable markets such as financial services (Non-Bank or insurance), or trucking.

```{r, eval=TRUE, tidy=TRUE}
# Make a histogram of the beta intervals created above
dfbeta_interval <- data.frame(table(unlist(beta_interval)))
names(dfbeta_interval) <- c("Interval", "Frequency")
hist(beta_interval, main = "Histogram of Beta Intevals",
     xlab = "Beta intervals", col = rgb(200, 50, 150, 100, maxColorValue = 255),
     border = NA) 

# Plot of Beta versus PE Ratio by given beta intervals
dat1 <- data.frame(PE = industries_only$Current.PE,
                   beta = industries_only$Average.Unlevered.Beta)
ggplot(dat1, aes(x = beta, y = PE)) +
    geom_line(stat = "identity", color = beta_interval) + 
    ggtitle("Beta vs PE Ratio") + theme_classic() + 
    scale_x_continuous(breaks = beta_intervals) + 
    scale_y_continuous(breaks = seq(from = 0, to = 1500, by = 100)) 
summary(industries_only$Current.PE)
```

Industries that have average betas of 0.9-1.2 (Interval 4) have higher PE ratios.

```{r, eval=TRUE, tidy=TRUE}
# Bar plot of Beta versus Expected Growth Rate in the Next 5 Years
dat2 <- data.frame(beta = clean_data$Average.Unlevered.Beta,
                   growth = clean_data$Expected.Growth.Next.5.Years)
ggplot(dat2, aes(x = beta, y = growth)) +
    geom_bar(position = "identity", stat = "identity") + 
    ggtitle("Beta vs Expected Growth Rate") +
    theme_classic()
```    

Industries with betas of around 1 have highter expected growth.

--------------- Michelle ----------------
```{r, eval=TRUE, tidy=TRUE}
# Density curve of Current PE and of Expected Growth in the Next 5 Years
plot(density(clean_data$Current.PE), main = "Density Plot of Current PE")
plot(density(clean_data$Expected.Growth.Next.5.Years),
     main = "Density Plot of Expected Growth in the Next 5 Years")

# Scatter plot of Current PE to Expected Growth in the Next 5 Years
plot(clean_data$Current.PE, clean_data$Expected.Growth.Next.5.Years,
     col = rgb(50, 200, 200, 100, maxColorValue = 255), pch = 16,
     bg = rgb(200, 200, 200, maxColorValue = 255),
     main = "Bar Plot of Forward PE Ratio")

# Make a linear regression of Current PE to Expected Growth in the Next 5 Years
fit1 <- lm(Expected.Growth.Next.5.Years ~ Current.PE, data = clean_data)
abline(fit1, col = rgb(50, 200, 200, maxColorValue = 255))
summary(fit1)

# Remove outliers and find the linear regression of Current PE to Expected
# Growth in the Next 5 Years
sorted_pe <- unlist(sort(clean_data$Current.PE,
                         decreasing = TRUE))
indices <- unlist(sort(clean_data$Current.PE,
                       decreasing = TRUE,
                       index.return = TRUE)[[2]])
sorted_growth <- clean_data$Expected.Growth.Next.5.Years[indices]
sorted_pe_growth <- data.frame(pe = sorted_pe, growth = sorted_growth)
dat3 <- subset(sorted_pe_growth, sorted_pe < 300)
plot(dat3$pe, dat3$growth, main = "Current PE Ratio vs. Expected Growth",
     xlab = "Current PE ratio", ylab = "Expected growth (next 5 years)",
     col = rgb(200, 50, 200, 100, maxColorValue = 255), pch = 16)
fit2 <- lm(growth ~ pe, data = dat3)
abline(fit2, col = rgb(200, 50, 200, maxColorValue = 255))
summary(fit2)

# Account for beta when sorting PE ratios and growth by taking the PE ratios
# and growths of industries with lower beta
sorted_beta <- unlist(sort(clean_data$Average.Unlevered.Beta,
                          index.return = TRUE)[[2]])
beta_pe <- clean_data$Current.PE[sorted_beta]
beta_growth <- clean_data$Expected.Growth.Next.5.Years[sorted_beta]
end <- length(beta_pe)
cutoff <- round(end/2)
beta1 <- data.frame(pe = beta_pe[1:cutoff], growth = beta_growth[1:cutoff])
plot(beta1$pe, beta1$growth, main = paste("Current PE Ratio vs. Expected Growth",
                                          "For Industries with Lower Beta"),
     xlab = "Current PE ratio", ylab = "Expected growth (next 5 years)",
     col = rgb(50, 50, 200, 100, maxColorValue = 255), pch = 16)
fit3 <- lm(growth ~ pe, data = beta1)
abline(fit3, col = rgb(50, 50, 200, maxColorValue = 255))
summary(fit3)

# Industries with lower beta
print("Industries with lower beta:")
print(clean_data$Industry[sorted_beta][1:cutoff])

# Account for beta when sorting PE ratios and growth by taking the PE ratios
# and growths of industries with higher beta
beta2 <- data.frame(pe = beta_pe[(cutoff+1):end],
                    growth = beta_growth[(cutoff+1):end])
plot(beta2$pe, beta2$growth, main = paste("Current PE Ratio vs. Expected Growth",
                                          "For Industries with Higher Beta"),
     xlab = "Current PE ratio", ylab = "Expected growth (next 5 years)",
     col = rgb(200, 50, 50, 100, maxColorValue = 255), pch = 16)
fit4 <- lm(growth ~ pe, data = beta2)
abline(fit4, col = rgb(200, 50, 50, maxColorValue = 255))
summary(fit4)

# Industries with higher beta
print("Industries with higher beta:")
print(clean_data$Industry[sorted_beta][(cutoff+1):end])

# Graph Current PE to Expected Growth in the Next 5 Years
ggplot(data = clean_data, aes(x = Current.PE,
                              y = Expected.Growth.Next.5.Years)) +
    geom_line(color = "#548edf") + xlab("Current PE") +
    ylab("Expected Growth in the Next 5 Years") +
    ggtitle("Plot of Current PE to Expected Growth") +
    theme_classic()

# Make a histogram of Current PE to Expected Growth for industries with
# growth, g, fulfilling g < 300
ggplot(dat3, aes(x = pe, y = growth)) + geom_line(color = "#ebcefb") +
    geom_bar(position = "identity", stat = "identity", color = "#000000") +
    ggtitle("Beta vs Expected Growth Rate") +
    theme_classic()

# Make a histogram of Current PE to Expected Growth for industries with
# growth, g, fulfilling 100 <= g < 200
dat4 <- subset(sorted_pe_growth, sorted_pe >= 100 & sorted_pe < 200)
ggplot(dat4, aes(x = pe, y = growth)) + geom_line(color = "#ebcefb") +
    geom_bar(position = "identity", stat = "identity", color = "#000000") +
    ggtitle("Beta vs Expected Growth Rate") +
    theme_classic()

# Make a histogram of Current PE to Expected Growth for industries
# with growth, g, fulfilling g < 100
dat5 <- subset(sorted_pe_growth, sorted_pe < 100)
ggplot(dat5, aes(x = pe, y = growth)) + geom_line(color = "#ebcefb") +
    geom_bar(position = "identity", stat = "identity",
             color = "#000000") +
    ggtitle("Beta vs Expected Growth Rate") + theme_classic()

# Make bubble plots of Current PE and Expected Growth in the
# Next 5 Years for different industries
symbols(industries_only$Current.PE,
        industries_only$Expected.Growth.Next.5.Years,
        circles = industries_only$Number.of.Firms,
        inches = 0.35, fg="white", bg="#facccc8d",
        xlab="Current PE", ylab="Expected Growth in 5 Years",
        main = "Current PE vs Expected Growth in the Next 5 Years")
text(industries_only$Current.PE, industries_only$Expected.Growth.Next.5.Years, 
     labels = industries_only$Number.of.Firms, cex = 0.2)

# Make bubble plots of Current PE and Expected Growth in the
# Next 5 Years for different industries accounting for outliers
industry_pe <- unlist(sort(industries_only$Current.PE, decreasing = TRUE))
industry_indices <- unlist(sort(industries_only$Current.PE, decreasing = TRUE,
                       index.return = TRUE)[[2]])
industry_growth <- industries_only$
    Expected.Growth.Next.5.Years[industry_indices]
industry_num_firms <- industries_only$Number.of.Firms[industry_indices]
industry_pe_growth <- data.frame(pe = industry_pe, growth = industry_growth,
                                 num_firms = industry_num_firms)
dat6 <- subset(industry_pe_growth, industry_pe < 150)
symbols(dat6$pe, dat6$growth, circles = dat6$num_firms,
        inches=0.35, fg="white", bg="#facccc8d",
        xlab="Current PE", ylab="Expected Growth in 5 Years",
        main = paste("Current PE Less Than 150 vs",
                     "Expected Growth in the Next 5 Years"))
text(dat6$pe, dat6$growth, labels = dat6$num_firms, cex = 0.3)
```

------------- Anais -------------------
Analysis of relationship between Average Unlevered Beta and Expected Growth for the next 5 years:

To investigrate the relationship between beta and expected growth over the next 5 years, the data required further cleaning. In order to run a regression between the two variables, the "%" signs in the values of the 5 year expected growth column were removed and the values were converted to numeric values. Using these values, a clean_data column "exp_growth" was aded to the dataframe "clean_data". 

```{r, tidy=TRUE}
# Graph the scatterplot of Unlevered Beta's impact on Expected Growth
# when accounting for their regression
reg1 <- lm(Expected.Growth.Next.5.Years ~ Average.Unlevered.Beta,
               data = clean_data)
summary(reg1)
ggplot(clean_data, aes(x = Average.Unlevered.Beta,
                       y = Expected.Growth.Next.5.Years)) +
    geom_point() + xlab("Average Unlevered Beta") +
    ylab("Expected Growth (%)") +
    geom_abline(aes(slope = unname(coef(reg1)["Average.Unlevered.Beta"]),
                    intercept = unname(coef(reg1)["(Intercept)"])),
                color = rgb(223, 84, 84, maxColorValue = 255)) +
    ggtitle("Average Unlevered Beta's Impact on Expected Growth") +
    theme_classic()
```

The regression returns the estimate for the coefficient of unlevered beta as 2.804, while the coefficient of the interecpt is 13.847. However, the summary of the regression, shows that regressing unlevered beta on exp_growth does not provide a good linear relationship between the two variables as the coefficient does not have linear statistical significance. 

The scatterplot of unlevered beta and expected growth further demonstrates the lack of a linear relationship between the two variables. We can see visually that the correlation between the two variables isn't strong. 

Further relationships were investigated as other variables that might be causing a deviation in the coefficient for the regression of unlevered beta and expected growth needed to be controlled for. 

One of these variables is the Price Earnings (P/E) ratio:

```{r, tidy=TRUE}
# Find the multivariate regression of expected growth to unlevered beta
# and current PE ratio
reg2 <- lm(Expected.Growth.Next.5.Years ~ Average.Unlevered.Beta +
               Current.PE, data = clean_data)
summary(reg2)

# Graph the scatterplot of unlevered beta's impact on expected growth
ggplot(clean_data, aes(x = Current.PE,
                       y = Expected.Growth.Next.5.Years)) +
    geom_point() + xlab("Current PE Ratio") + ylab("Expected Growth (%)") +
    ggtitle("Scatterplot of PE Ratio vs Expected Growth") +
    theme_classic()
```

The summary of this regression also demonstrates that there isn't a significant linear relationship between these variables as the only statistically significant coefficient is that of the intercept. 

Again, having a look at the relationship visually through the ggplot, we see that there isn't a strong linear relationship and there are outliers present. (#####ASK PETER######)

These were interesting findings, which led to the investigration of other related variables, such as the PEG Ratio. The Price/Earnings to Growth (PEG) is a stock's price-to-earnings ratio divided by the growth rate of its earnings for a specified time period. The PEG ratio is used to determine a stock's value while taking the company's earnings growth into account, and is considered to provide a more complete picture than the P/E ratio. 

This next regression checks for a linear relationship between PEG ratio and exp_growth, meanwhile retaining PE ratio and unlevered beta in the regression to eliminate any possible  effects of confounding factors. 

```{r, tidy=TRUE}
# Graph the scatterplot of PEG ratio's impact on expected growth after
# finding the multivariate regression of expected growth in the next 5
# years to average unlevered beta, the current PE ratio, and the PEG Ratio.
# The graph only concerns the regression of expected growth to beta.
reg3 <- lm(Expected.Growth.Next.5.Years ~ Average.Unlevered.Beta +
               Current.PE + PEG.Ratio, data = clean_data)
summary(reg3)
ggplot(clean_data, aes(x = Current.PE,
                       y = Expected.Growth.Next.5.Years)) +
    geom_point() + xlab("Current PE Ratio") + ylab("Expected Growth (%)") +
    geom_abline(aes(slope = unname(coef(reg3)["Average.Unlevered.Beta"]),
                    intercept = unname(coef(reg3)["(Intercept)"])),
                color = rgb(223, 84, 84, maxColorValue = 255)) +
    ggtitle("PEG Ratio's Impact on Expected Growth") +
    theme_classic()
```

The summary of regressing PEG ratio against the expected growth, shows that there is statistical significance to the coefficients. The linear regression returned a coefficient estimate of approximately -1.376 for the PEG ratio and 16.472 for the intercept. The summary shows that the PEG ratio estimate has statistical significance at the ????????? level. (####ASK PETER#####)

Having a look at the relationship through a graphical respresentation, the function abline was used to draw the best fit regression line. 

```{r, tidy=TRUE}
# Graph the scatterplot of PEG ratio's impact on expected growth and the
# regression line of expected growth to PEG ratio and the regression line
# of the multivariate regression found in reg3
reg4 <- lm(Expected.Growth.Next.5.Years ~ PEG.Ratio, data = clean_data)
summary(reg4)
ggplot(clean_data, aes(x = PEG.Ratio,
                       y = Expected.Growth.Next.5.Years)) +
    geom_point() + xlab("PEG Ratio") + ylab("Expected Growth (%)") +
    geom_abline(aes(slope = unname(coef(reg3)["PEG.Ratio"]),
                    intercept = unname(coef(reg3)["(Intercept)"])),
                color = rgb(84, 233, 233, maxColorValue = 255)) +
    geom_abline(aes(slope = unname(coef(reg4)["PEG.Ratio"]),
                    intercept = unname(coef(reg4)["(Intercept)"])),
                color = rgb(223, 84, 84, maxColorValue = 255)) +
    ggtitle("PEG Ratio's Impact on Expected Growth") +
    theme_classic()
```

The negative relationship between PEG Ratio and Expected Growth makes sense as the lower the PEG Ratio the higher the growth will be. PEG Ratio is used for stock valuation and is defined as P/E Ratio / Growth. For a good stock you would want a small P/E Ratio and a high denominator as Growth, resulting in a small PEG Ratio. 

library(scatterplot3d)
scatterplot3d(x = clean_data$Expected.growth.in.next.5.years, clean_data$PEG.Ratio, z = clean_data$Average.Unlevered.Beta, angle = 280, scale.y = .3, xlab = "Expected Growth in Next 5 Years", ylab = "PE Ratio", zlab = "Beta")

Although there is a wide range of industries that have various values of expected growth (thus showing no correlation along with beta and PE ratio), we are still able to see the effects of beta on PE Ratio. As beta increases, PE ratio decreases.

-------------------- Christian -----------------------
Correlation between Trailing PE and Forward PE
```{r, eval=TRUE}

# Impact on Trailing PE on Forward PE
plot(clean_data$Trailing.PE, clean_data$Forward.PE,
     xlab = "Trailing PE", ylab = "Forward PE",
     main = "Correlation Between Trailing PE and Forward PE",
     col = '#4876FF')

# Impact on Forward PE on Trailing PE
plot(clean_data$Forward.PE, clean_data$Trailing.PE,
     xlab = "Forward PE", ylab = "Trailing PE",
     main = "Correlation Between Trailing PE and Forward PE",
     col = '#2E8B57')

```

Analysis: I plotted the data for trailing price earnings and forward price earnings on a scatterplot in order to see the impact of trailing price earnings on forward price earnings, and the impact of forward price earnings on trailing price earnings. Based on the graph that is depicted by the code above, there is a positive correlation between the trailing price earnings and the forward price earnings. This means that the forward price earnings increases as the trailing price earnings increases, and vise versa (though the correlation when the variables are swtiched is not that strong, meaning that the positive impact on the forward price earnings on the trailing price earnings is not as strong as the positive impact that the traling price earnings has on forward price earnings).


Correlation between Beta and PE Ratio
```{r, eval=TRUE}

# Impact of Beta on PE Ratio
plot(clean_data$Average.Unlevered.Beta, clean_data$PEG.Ratio,
     xlab = "Average Unlevered Beta", ylab = "PE Ratio",
     main = "Correlation Between Beta and PE Ratio",
     col = "#FF0000")

# Impact of PE Ratio on Beta
plot(clean_data$PEG.Ratio, clean_data$Average.Unlevered.Beta,
     xlab = "PE Ratio", ylab = "Average Unlevered Beta",
     main = "Correlation Between PE Ratio and Beta",
     col = '#8B0000')

```

Analysis: I plotted the data for the average unlevered beta and price earnings (PE) ratio on a scatterplot in order to see the impact of average unlevered beta on the price earnings ratio, and the impact of the price earnings ratio on the average unlevered beta. Based on the graph that is depicted by the code above, there is almost no correlation between the average unlevered beta and the price earnings ratio. This means that the average unlevered beta has no effect on the price earnings ratio in most instances. In contrast, there is a positive correlation between the price earnings ratio and the average unlevered beta. This means that the PE ratio has a positive effect of the average unlevered beta.


Correlation Between Trailing PE and the Expected Growth in the Next 5 Years
```{r, eval=TRUE}

# Impact of Trailing PE on Expected Growth in the Next 5 Years
plot(clean_data$Trailing.PE, clean_data$Expected.Growth.Next.5.Years,
     xlab = "Trailing PE", ylab = "Expected Growth in the Next 5 Years",
     main = paste("Correlation Between Traling PE and Expected",
                  "Growth in the Next 5 Years"), col = '#551A8B')

# Impact of Expected Growth in the Next 5 Years on Trailing PE
plot(clean_data$Expected.Growth.Next.5.Years, clean_data$Trailing.PE,
     xlab = "Expected Growth in the Next 5 Years", ylab = "Trailing PE",
     main = paste("Correlation Between Expected Growth in the",
                  "Next 5 Years and Trailing PE"), col = '#27408B')

```

Analysis: I plotted the data for trailing price earnings and the expected growth in the next five years on a scatterplot in order to see the impact of trailing price earnings on the expected growth in the next five years, and the impact of the expected growth in the next five years on trailing price earnings. Based on the graphs above, there are no correlations to be found between trailing PE and the expected growth in the next five years. In other words, the trailing PE has no effect on the expected growth in the next five years, and vise versa.


Scatterplot from Multiple Angles: Correlations between Expected Growth, PE Raio, and Beta
```{r, eval=TRUE}

# Multiple angles
scatterplot3d(x = clean_data$Expected.Growth.Next.5.Years,
              clean_data$PEG.Ratio, z = clean_data$Average.Unlevered.Beta,
              angle = 30, scale.y = .3,
              xlab = "Expected Growth in Next 5 Years",
              ylab = "PE Ratio", zlab = "Beta")

# Look at PE Ratio here:
scatterplot3d(x = clean_data$Expected.Growth.Next.5.Years,
              clean_data$PEG.Ratio, z = clean_data$Average.Unlevered.Beta,
              angle = 280, scale.y = .3,
              xlab = "Expected Growth in Next 5 Years",
              ylab = "PE Ratio", zlab = "Beta")

scatterplot3d(x = clean_data$Expected.Growth.Next.5.Years,
              y = clean_data$PEG.Ratio,
              z = clean_data$Average.Unlevered.Beta,
              angle = 200, scale.y = .3,
              xlab = "Expected Growth in Next 5 Years",
              ylab = "PE Ratio", zlab = "Beta")
scatterplot3d(x = clean_data$Expected.Growth.Next.5.Years,
              y= clean_data$PEG.Ratio,
              z = clean_data$Average.Unlevered.Beta,
              angle = 230, scale.y = .3,
              xlab = "Expected Growth in Next 5 Years",
              ylab = "PE Ratio", zlab = "Beta")
scatterplot3d(x = clean_data$Expected.Growth.Next.5.Years,
              y = clean_data$PEG.Ratio,
              z = clean_data$Average.Unlevered.Beta,
              angle = -400, scale.y = .3,
              xlab = "Expected Growth in Next 5 Years",
              ylab = "PE Ratio", zlab = "Beta")
scatterplot3d(x = clean_data$Expected.Growth.Next.5.Years,
              y= clean_data$PEG.Ratio,
              z = clean_data$Average.Unlevered.Beta,
              angle = 200, scale.y = .3,
              xlab = "Expected Growth in Next 5 Years",
              ylab = "PE Ratio", zlab = "Beta")

```

Analysis: I used a scatterplot in order to see the correlations between all of the variables when they are all present within the same graph. As a result of including all of the variables in one graph rather than having them in separate regressions, I am able to produce more accurate result when analyzing the impacts of growth and beta on the price earnings ratios. Although there is a wide range of industries that have various values of expected growth (thus showing no correlation along with beta and the price earnings ratio), we are still able to see the effects of beta on the price earnings ratio. There is an inverse correlation between the price earnings ratio and beta, since the price earnings ratios decreases when beta increases. In other words, beta has a negative impact on the price earnings ratios.

#Findings
```{r}
```

#Conclusion

write.
